\documentclass[../main.tex]{subfiles}

\begin{document}

\chapter*{Références bibliographiques}
\addcontentsline{toc}{chapter}{Références bibliographiques}

\begin{thebibliography}{99}

\bibitem[Atlas Magazine(2023)]{AtlasMagazine2023}
Atlas Magazine (2023).
\newblock \emph{Panorama des marchés africains de l'assurance 2023}.
\newblock Casablanca: Atlas Magazine.

\bibitem[Banque Mondiale(2023)]{BanqueMondiale2023}
Banque Mondiale (2023).
\newblock \emph{Worldwide Governance Indicators (WGI)}.
\newblock Washington D.C.: Banque Mondiale.
\newblock \url{https://info.worldbank.org/governance/wgi/}

\bibitem[Beck et Webb(2003)]{Beck2003}
Beck, T. et Webb, I. (2003).
\newblock Economic, demographic, and institutional determinants of life insurance
  consumption across countries.
\newblock \emph{World Bank Economic Review}, 17(1), 51--88.

\bibitem[Breiman(2001)]{Breiman2001}
Breiman, L. (2001).
\newblock Random forests.
\newblock \emph{Machine Learning}, 45(1), 5--32.

\bibitem[Chinn et Ito(2006)]{ChinnIto2006}
Chinn, M.\,D. et Ito, H. (2006).
\newblock What matters for financial development? Capital controls, institutions,
  and interactions.
\newblock \emph{Journal of Development Economics}, 81(1), 163--192.

\bibitem[CIMA(2023)]{CIMA2023}
CIMA (2023).
\newblock \emph{Code des assurances des États membres de la CIMA}.
\newblock Mise à jour 2023.

\bibitem[Eling et Schmit(2012)]{Eling2012}
Eling, M. et Schmit, J.\,T. (2012).
\newblock Is there market discipline in the European insurance industry?
\newblock \emph{The Geneva Papers on Risk and Insurance}, 37(1), 180--207.

\bibitem[FANAF(2023)]{FANAF2023}
FANAF (2023).
\newblock \emph{Statistiques du marché africain de l'assurance, exercice 2022--2023}.
\newblock Dakar: Fédération des Sociétés d'Assurances de Droit National Africaines.

\bibitem[FMI(2024)]{FMI2024}
Fonds Monétaire International (2024).
\newblock \emph{World Economic Outlook Database}, octobre 2024.
\newblock Washington D.C.: FMI.
\newblock \url{https://www.imf.org/external/datamapper/}

\bibitem[Friedman(2001)]{Friedman2001}
Friedman, J.\,H. (2001).
\newblock Greedy function approximation: a gradient boosting machine.
\newblock \emph{Annals of Statistics}, 29(5), 1189--1232.

\bibitem[Guerard et al.(2021)]{Guerard2021}
Guerard, Y., Nabeth, M. et Monkam, D. (2021).
\newblock Multicriteria framework for insurance market entry decisions in emerging
  economies: Application to Sub-Saharan Africa.
\newblock \emph{The Geneva Papers on Risk and Insurance}, 46(3), 412--438.

\bibitem[Ke et al.(2017)]{Ke2017}
Ke, G., Meng, Q., Finley, T., Wang, T., Chen, W., Ma, W., Ye, Q. et Liu, T.-Y. (2017).
\newblock LightGBM: A highly efficient gradient boosting decision tree.
\newblock \emph{Advances in Neural Information Processing Systems}, 30, 3146--3154.

\bibitem[NAICOM(2022)]{NAICOM2022}
NAICOM (2022).
\newblock \emph{Nigerian Insurance Industry Annual Report 2022}.
\newblock Abuja: National Insurance Commission.

\bibitem[Outreville(2013)]{Outreville2013}
Outreville, J.\,F. (2013).
\newblock The relationship between insurance and economic development:
  85 empirical papers for a review of the literature.
\newblock \emph{Risk Management and Insurance Review}, 16(1), 71--122.

\bibitem[Swiss Re Institute(2023)]{SwissRe2023}
Swiss Re Institute (2023).
\newblock \emph{World Insurance Report -- Sigma}, no.\,3/2023.
\newblock Zurich: Swiss Re.

\end{thebibliography}

\clearpage

% ============================================================
%  ANNEXES
% ============================================================
\appendix


\end{document}
